\documentclass[a4paper,11pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular}
\usepackage{multirow}                   %for Grades
\usepackage{titlesec}					%custom \section
\usepackage{longtable}
\usepackage{enumitem}% http://ctan.org/pkg/enumitem

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks, breaklinks, urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
    SmallCapsFont = Fontin-SmallCaps.otf,
    BoldFont = Fontin-Bold.otf,
    ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge Stephen Kent \textsc{Bailey}
	}\\ \medskip}
\centering{
    \href{https://stkbailey.github.io}{stkbailey.github.io} $\bullet$ \href{mailto:stkbailey@gmail.com}{stkbailey@gmail.com}
}\\ \medskip
\parbox{12.2cm}{\centering{
    \small{ \emph{ Rigorous scientist with expertise in image processing, data visualization, and statistics. Looking to create value from big, messy data. Expect to: Take ownership. Drive towards results. Put team first. Always ask questions. Improve every day. }}
}}


%--------------------SECTIONS----------------------------------
\section{Education \& Skills}
\begin{tabular}{rp{11cm}}	

    \textsc{Exp.} 2018 & \textsc{Ph.D.} in \textsc{Cognitive Neuroscience}, \textbf{Vanderbilt University} \smallskip \\
    
    2011 & \textsc{B.S. in Chemistry} and \textsc{B.A. in Philosophy}, \textbf{Samford University} \smallskip \\

    \textsc{Software} & \small{Python (esp. scipy, pandas, matplotlib, scikit-learn), Keras, Ubuntu, bash, Microsoft Power BI and all Office products,  SQL, Docker, R, Linux} \\


\end{tabular}


\section{Work Experience}
\begin{longtable}{r|p{11cm}}
 	\emph{Current} & NIH Research Fellow at \textsc{Vanderbilt University} \\*
 	2013 & \small{\emph{Pushed lab in novel direction  through use of graph theory to model brain "connectome" throughout the lifespan. Research featured in talks at two major international conferences. }}	\href{https://ww5.aievolution.com/hbm1801/index.cfm?do=ev.viewEv&ev=1362}{\color{blue}\Mundus} \footnotesize{
 	\begin{itemize}[itemsep=1pt,topsep=2pt]
    	\item Leveraged high performance computing cluster to streamline analyses, reducing human wait time from \textgreater 1 week to \textless 1 hour.
    	\item Upgraded lab imaging database of 13,000+ scans by directing its migration to web-based storage platform (XNAT).
    	\item Analyzed data with a variety of techniques, including support vector machines, GLM, ICA/PCA, graph theory, and timeseries analysis.
	\end{itemize} } \\*
	\multicolumn{2}{c}{}\\
    
    
	\emph{Current} & Data Science Intern at \textsc{Nashville Biosciences} \\*
	2018 & \small{\emph{Developed core application for patent-pending "text readability" algorithm in Python.}}
	\footnotesize{
	\begin{itemize}[itemsep=1pt,topsep=2pt]
	    \item Used \textit{natural language processing} tools (Word2Vec, FreqDict, Stemmers) to analyze documents.
	    \item Algorithm and database were wrapped into Django SaaS application.
    \end{itemize}}\\*
	\multicolumn{2}{c}{} \\
 	
    
	2017 & App Developer at \textsc{Vanderbilt Center for Tech Transfer} \\*
	& \small{\emph{Developed core application for patent-pending "text readability" algorithm in Python.}}
	\footnotesize{
	\begin{itemize}[itemsep=1pt,topsep=2pt]
	    \item Used \textit{natural language processing} tools (Word2Vec, FreqDict, Stemmers) to analyze documents.
	    \item Algorithm and database were wrapped into Django SaaS application.
    \end{itemize}}\\*
 	\multicolumn{2}{c}{} \\



    2017 & Data Analyst at \textsc{Metro Nashville Public Schools} \\*
    \textsc{May} 2017 & \small{\emph{Built interactive reports on teacher vacancies that transformed communication between central office staff and 130+ school leaders.} \href{https://app.powerbi.com/view?r=eyJrIjoiZWVhMmIxMjUtOGM1Yi00MzQ4LWE4M2UtMzVlODA4N2NkNTVmIiwidCI6ImM2ODI4MjU3LTY0MTAtNDA3ZS1iNTU3LWI1ZGM3MjExZGU1NSIsImMiOjN9}{\color{blue}\Mundus}}
    \footnotesize{
    \begin{itemize}[itemsep=1pt,topsep=2pt]
        \item Honed communication skills with multiple audiences, including executive leadership.
        \item Created data dictionary for clarifying internal discussions about critical terms, such as "retention" and "termination".
    \end{itemize}}\\*
    \multicolumn{2}{c}{}\\

    2013 & Director of Technology at \textsc{Teach For America - Delta Institute} \\*
    & \small{\emph{Led four-person team delivering print, copy, and technology support services to 800+ teachers during intense 5-week summer institute.}}
    \footnotesize{
    \begin{itemize}[itemsep=1pt,topsep=2pt]
        \item Led four-person team through and regular meetings. \href{...}{\color{blue}\Mundus}
        \item Improved upon previous year's satisfaction ratings by 10\%. 
    \end{itemize}}\\
    \multicolumn{2}{c}{} \\

    2013 & Manager of Regional Operations at \textsc{Teach For America - Alabama} \\*
    2011 & \small{\emph{Managed teacher hiring and on-boarding processes, grant compliance, and financial tracking and reimbursement systems. Delivered results within a fast-paced, start-up environment, as the region grew from supporting 30 teachers to more than 170.}}
    \footnotesize{
    \begin{itemize}
        \item Promoted after first year, reflecting superior performance and additional people-management responsibilities
        \item Developed first-of-its-kind online learning course to facilitate onboarding of new teachers, contributing to top teacher retention rates in the country.
        \item Oversaw \$119,000 Americorps grant and managed relationships with key parties. Awarded an additional \$66,000 in my 2nd year, a 55\% increase over first year.
        \item Designed year-long orientation program to support more than 80 incoming teachers with the transition to Alabama, including creating 10 online training presentations, 4 annual recruitment campaigns, and week-long orientation program.
        \item Organized logistics of two week-long conferences for more than 90 attendees and more than 10 other large professional development events.
    \end{itemize}
    } \\*
\end{longtable}


\section{Presentations and Teaching}
\begin{longtable}{rp{11cm}}
    \textsc{Aug.} 2018 & \textsc{Biomedical Imaging Analysis in Python} | \href{https://www.datacamp.com/courses/biomedical-image-analysis-in-python}{DataCamp.com} \\
    & \small{\emph{An introduction to the principles of computer vision for DataCamp.com}} \smallskip \\

    \textsc{June} 2018 & \textsc{Reorganization of Resting-State Networks during Reading and Listening: a dvelopmental perspective} \\
    & \small{\emph{Invited talk at the 2018 Human Brain Mapping meeting} | \href{https://ww5.aievolution.com/hbm1801/index.cfm?do=ev.viewEv&ev=1362}{Program}} \smallskip \\

    \textsc{April} 2018 & \textsc{Deconvoluting Convolutions: U-Nets for Object Detection}\\
    & \small{\emph{Presentation delivered to the \href{https://www.meetup.com/Data-Science-Nashville/events/249853957/}{\textsc{Nashville Data Science Meetup}.} | \href{https://github.com/stkbailey/deconv-conv)}{Repo}}} \smallskip \\

    \textsc{Feb.} 2018 & \textsc{Principles of Network Analysis with NetworkX}\\
    & \small{\emph{Tutorial delivered at the \textsc{PyTennessee} regional conference. | \href{https://github.com/stkbailey/nashnetx/presentations}{Repo}}}  \smallskip\\

    \textsc{Aug. 2016} & \textsc{Lead ELL Instructor} at \textsc{Conexi\'on Am\'ericas} \\
    & \small{\emph{Volunteer instructor for course catered to immigrants and refugees.}} \\ 
    
    \textsc{Aug. 2014} & \textsc{Graduate Teaching Assistant} for at \textsc{Vanderbilt University} \\
    & \small{\emph{Assisted course instruction and grading for the graduate class, \textit{SPED 7410: Teaching Reading to Students with Severe and Persistent Academic and Behavior Difficulties}}.} \\ 
    
\end{longtable}


\section{Honors, Awards, Accomplishments}
\begin{longtable}{rp{11cm}}
	\textsc{May} 2016 & Won a competitive textsc{NIH F31 research fellowship}. \href{https://projectreporter.nih.gov/project_info_description.cfm?aid=9328269&icde=35806628}{\color{blue}\Mundus} \smallskip \\

    \textsc{Ongoing} & Author on 8 research papers (3 first author) published in high-impact journals. \href{https://scholar.google.com/citations?user=s3nPF1MAAAAJ&hl=en}{\color{blue}\Mundus} \smallskip \\

    \textsc{Aug.} 2018 & Awarded textsc{Insight Data Science} fellowship. \smallskip \\

    \textsc{April} 2018 & \textsc{Most Impactful Kernel} for \textsc{Kaggle's Data Science Bowl} \href{https://www.kaggle.com/c/data-science-bowl-2018/discussion/54797}{\color{blue}\Mundus}. \smallskip \\

    \textsc{March} 2018 & Finalist in Vanderbilt's \textsc{3 Minute Thesis} competition. \href{	https://news.vanderbilt.edu/2018/03/26/ph-d-student-argues-for-early-intervention-in-reading-trouble-takes-3mt-top-prize/}{\color{blue}\Mundus} \smallskip \\

    \textsc{Sept.} 2016 & Won \href{https://projectreporter.nih.gov/project_info_description.cfm?aid=9328269&icde=35806628}{\textsc{NIH F31 National Research Service Award}}, highly competitve fellowship for predoctoral students, valued at more than \$90,000. \smallskip \\
    
    \textsc{June} 2013 & Scored in the 99th percentile overall of the {\textsc{GRE}\textregistered}\setmainfont[SmallCapsFont=Fontin-SmallCaps.otf]{Fontin.otf}: 730 (\textsc{q:50;v:39}) 98\textsuperscript{th} percentile; (89\textsuperscript{th} percentile) \smallskip \\

    \textsc{May 2011} & Awarded \textsc{Omicron Delta Kappa}'s \href{https://odk.org/wp-content/uploads/2018/01/Scholarship-Opportunities-List.pdf}{John D. Morgan Scholarship}, given out to the "top overall undergraduate applicant" in ODK. \smallskip \\

	\textsc{May} 2011 & Winner of \href{https://www.samford.edu/news/2011/Samford-Students-Cited-for-Service-Leadership}{\textsc{Samford University's Service Award}}, awarded to one senior for "best exemplifying qualities of social service". \smallskip \\
	
    \textsc{May} 2011 & Winner of \textsc{Samford's Greek Man of the Year} award, given to one man for embodying the ideals of Greek excellence.\\

\end{longtable}


\section{Other Projects and activities}
\begin{tabular}{rp{11cm}}
    \textsc{Oct.} 2017 & Co-founder of \textsc{Nashville Data Nerds} \href{https://www.meetup.com/Data-Nerds/}{MeetUp} \\
    & \small{\emph{Fostering a data science community in Nashville}} \smallskip \\

    \textsc{Aug. 2014} & V.P. of Education for \textsc{Vanderbilt Toastmasters} \\
    & \small{\emph{Sharpening speaking techniques and supporting others' development.}} \\
\end{tabular}


\section{Software}
\begin{longtable}{rp{11cm}}
\end{longtable}


\section{Selected Publications}
\begin{tabular}{rp{12cm}}
    \multicolumn{2}{l}{\textit{For a full list, please see my citations on \href{https://scholar.google.com/citations?user=s3nPF1MAAAAJ&hl=en}{Google Scholar}.}} \smallskip \\
    
    \textsc{In press} & Bailey et al. Applying a network framework to the neurobiology of reading and dyslexia. \emph{Journal of Neurodevelopmental Disabilities}. \smallskip \\

    \href{http://www.pnas.org/content/early/2017/12/26/1711567115.long}{2018} & Ding et al. Detection of synchronous brain activity in white matter tracts at rest and under functional loading. \emph{PNAS}. \smallskip \\

    \href{http://www.jneurosci.org/content/37/35/8549}{2017} & Wendelken et al. Fronto-parietal structural connectivity predicts development of functional connectivity and reasoning. \emph{Journal of Neuroscience} \smallskip \\

    \href{https://link.springer.com/article/10.1007/s11881-015-0114-y}{2016} & Bailey et al. Anomalous gray matter patterns in specific reading comprehension deficits are independent of dyslexia. \emph{Annals of Dyslexia}. \smallskip \\

    \href{https://www.pdcnet.org/scholarpdf/show?id=stance_2011_0004_0015_0026&pdfname=stance_2011_0004_0015_0026.pdf&file_type=pdf}{2011} & Bailey. Certainly Uncertain: Nietzchean Pessimism for an Optimistic World. \emph{Stance}. \\

\end{tabular}



\end{document}
